---
title: Googlesheets demo
---

<!-- Make sure to run R/googlesheets_setup.R first -->

```{r setup}
library(here)
library(googlesheets)
library(knitr) # brings kable() into namespace
library(kableExtra)
library(dplyr)
library(ggplot2)
```

## Load data from a googlesheet

Read in the google access token we created with googlesheets_setup.R
```{r}
gs_auth(token = here::here("googlesheets_token.rds"))
```


Now we can list the googlesheets that we have access to
```{r}
#gs_ls()
```

Gives the information about the googlesheet from a url
```{r}
resbaz_url <- "https://docs.google.com/spreadsheets/d/1GEVg2qVLyEO8si8WwXNx0O85vfxaL1-GTC_m50Q0R9s"
(resbaz_sheet_info <- gs_url(resbaz_url))
```

Now we can read that sheet in 
```{r}
resbaz <- gs_read(resbaz_sheet_info)
head(resbaz)
```


## Data analysis

Lets look at some summaries of the data

```{r}
resbaz %>% group_by(Session) %>% tally()
```


Looks like there are some NAs

Lets find out if our NAs are in the data we care about
```{r}
resbaz %>% filter(is.na(topic_intimidation_before) | is.na(topic_intimidation_after)) %>% group_by(Session) %>% tally()
```
Looks like we can safely remove them

```{r}
# remove rows where both topic intimidations are not NA
resbaz_filt <- resbaz %>% filter(!is.na(topic_intimidation_before) & !is.na(topic_intimidation_after) & !is.na(Session))
```



```{r}
resbaz_filt %>% group_by(topic_intimidation_before) %>% tally()
```




```{r}
resbaz_filt %>% group_by(topic_intimidation_after) %>% tally()
```

So now we can make a table using kable
```{r}
resbaz_filt %>% group_by(Session) %>% tally() %>% kable()
```

We could make the same table and add on information about the "intimidation change" by session.

```{r}
session_n <- resbaz_filt %>% group_by(Session) %>% tally()
intim_delta <- resbaz_filt %>% mutate(delta = topic_intimidation_before - topic_intimidation_after) %>% group_by(Session) %>% summarise(mean_before= mean(topic_intimidation_before), mean_after = mean(topic_intimidation_after), mean_delta = mean(delta))
```


```{r}
full_join(session_n, intim_delta, by = "Session") %>% #join the tables onto each other
  kable(., digits = 2, format = 'html') %>% kableExtra::add_header_above(c("","", "Topic Intimidation" =3))
```

How about we add some groups to separate SWC from the others and make it the full width.

```{r}
full_join(session_n, intim_delta, by = "Session") %>% #join the tables onto each other
  arrange(desc(Session)) %>%  # will bring SWC to top
  kable(., digits = 2, format = 'html') %>%
  kable_styling(full_width = TRUE) %>% 
  kableExtra::add_header_above(c("","", "Topic Intimidation" =3)) %>%
  kableExtra::group_rows("SWC",1, 5) # group is rows 1-5 inclusive
```

